---
title: "Haoyuan"
author: "Haoyuan"
date: "11/18/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# install.packages('tidyverse')
# install.packages('ggcorrplot')
# install.packages('clustertend')
# install.packages('gridExtra')
# install.packages('ggplot2')
# install.packages('arules')
# install.packages('arulesViz')


# import library
library(tidyverse)
library(ggcorrplot)
library(clustertend)
library(gridExtra)
library(ggplot2)
library(arules)
library(arulesViz)

# summary function
# for numeric attributes
summarize_numeric = function(dataset) {
    dataset = select_if(dataset, is.numeric)
    summary.table = data.frame(Attribue = names(dataset))
    summary.table = summary.table %>% 
        mutate('Missing Values' = apply(dataset, 2, function(x) sum(is.na(x))),
               'Unique Values' = apply(dataset, 2, function(x) length(unique(x))),
               'Mean' = round(colMeans(dataset, na.rm = TRUE),2),
               'Min' = apply(dataset, 2, function(x) min(x, na.rm = TRUE)),
               'Max' = apply(dataset, 2, function(x) max(x, na.rm = TRUE)),
               'SD' = round(apply(dataset, 2, function(x) sd(x, na.rm = TRUE)),2))
    summary.table
    }

# for character attributes
summarize_character = function(dataset) {
    dataset = select_if(dataset, is.character)
    summary.table = data.frame(Attribue = names(dataset))
    summary.table = summary.table %>% 
        mutate('Missing Values' = apply(dataset, 2, function(x) sum(is.na(x))),
               'Unique Values' = apply(dataset, 2, function(x) length(unique(x))))
    summary.table
}

# winsorize
winsorize = function(data, end){
  endpoint = quantile(data, probs=c(end, 1-end), na.rm = T)
  data[data < endpoint[1]] = endpoint[1]
  data[data > endpoint[2]] = endpoint[2]
  return(data)
}

```

# DATA PROCESSING

```{r}
#Libraries
library(readr)
library(dplyr)

folder_name = "diabetes+130-us+hospitals+for+years+1999-2008/"
file_name = c("diabetic_data.csv", "IDS_mapping.csv")

#Dataset
diabetic_data = read_csv(paste(folder_name, file_name[1], sep = ''))
IDS_mapping = read_csv(paste(folder_name, file_name[2], sep = ''))

diabetic_data
IDS_mapping
```

```{r}
#Reform IDS Mapping
##Split the IDS Mapping
split_indices = c(0, which(is.na(IDS_mapping$admission_type_id)), nrow(IDS_mapping) + 1)
split_data = lapply(  seq_along(split_indices[-1])
                    , function(i) { start_index <- split_indices[i] + 1
                                    end_index <- split_indices[i + 1] - 1
                                    IDS_mapping[start_index:end_index, , drop = FALSE]
                                  }
                    )

split_data = lapply(split_data, as.data.frame)

rm(split_indices)

##Remove the first row because it was the column name
for (i in seq_along(split_data)[-1]) {
  colnames(split_data[[i]])[1] <- split_data[[i]][1, 1]
  split_data[[i]] <- dplyr::slice(split_data[[i]], -1)
}
rm(i)

##Make the first column a numeric type
split_data <- lapply(split_data, function(df) {
  df[[1]] <- as.numeric(df[[1]])
  return(df)
})

##Split the list into separate dataframes
names(split_data) <- c("admission_type_id", "discharge_disposition_id", "admission_source_id")
list2env(split_data, envir = .GlobalEnv)

##Remove Redundant Data
# rm(split_data)
rm(IDS_mapping)

admission_type_id
discharge_disposition_id
admission_source_id

```

```{r}

# df = merge(diabetic_data, admission_type_id, by.x = "admission_type_id", by.y = "admission_type_id", all.x =TRUE)
# names(df)[names(df) == "description"] <- "admission_type_description"
# df = df[, -which(names(df) == "admission_type_id")]
# df = diabetic_data

for (i in c("admission_type_id", "discharge_disposition_id", "admission_source_id")) {
  diabetic_data = merge(diabetic_data, split_data[[i]], by.x = i, by.y = i, all.x =TRUE)
  names(diabetic_data)[names(diabetic_data) == "description"] = paste(substr(i, start = 1, stop = nchar(i) - 3), "description", sep="_") 
  diabetic_data = diabetic_data[, -which(names(diabetic_data) == i), drop = FALSE]
}

diabetic_data


```
```{r}
#Reform Diabetic Data 
##Replace "?" values to NA
diabetic_data[diabetic_data == "?"] = NA

diabetic_data
```

```{r data review}

# next step: identify if an attribute is really a char or num

df = diabetic_data
# df$encounter_id
df$encounter_id = as.character(df$encounter_id)
df$patient_nbr = as.character(df$patient_nbr)
df
summarize_numeric(df)
summarize_character(df)
# initial data review
class(diabetic_data)
str(diabetic_data)
names(diabetic_data)
summarize_numeric(diabetic_data)
summarize_character(diabetic_data)

```
```{r}
missing_percentage <- sapply(diabetic_data, function(x) sum(is.na(x)) / length(x) * 100)

missing_data_summary <- data.frame(Column = names(missing_percentage), Percentage = missing_percentage)
missing_data_summary <- missing_data_summary[missing_data_summary$Percentage != "0", ]
print(missing_data_summary)
```


```{r}
# other data processing

# will remove weight, payer_code, medical_specialty


df = diabetic_data

df = df %>% 
  # na.omit() %>% # drop missing value
  select(!c(  weight
            , payer_code
            , medical_specialty
            )
         ) # drop irrelevant attributes

# all num attributes


# all char attributes


# Patient Info

# Identifiers
patient_nbr
encounter_id

dff = df %>% group_by(patient_nbr) %>% count() %>% arrange(desc(n))

ggplot(df) + geom_bar(aes(x = patient_nbr))

ggplot(dff) + geom_histogram(aes(x = patient_nbr, y = n), bins = 5)

ggplot(df, aes(x = reorder(patient_nbr, -table(patient_nbr)[patient_nbr]))) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  xlab("patient_nbr") +
  ylab("Count") +
  expand_limits(y = c(1,30))

# Race
ggplot(df, aes(x = reorder(race, -table(race)[race]))) +
  geom_bar() +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  xlab("Race") +
  ylab("Count") +
  expand_limits(y = c(1,80000))
ggplot(df, aes(x = reorder(race, -table(race)[race]))) +
  geom_bar() +
  geom_text(stat='count', aes(label = scales::percent(round((..count..)/sum(..count..),5))), vjust=-1) +
  xlab("Race") +
  ylab("Count") +
  expand_limits(y = c(1,80000))


ggplot(df) + geom_bar(aes(x = gender))
ggplot(df) + geom_bar(aes(x = age))
ggplot(df) + geom_bar(aes(x = diag_1))
ggplot(df) + geom_bar(aes(x = diag_2))
ggplot(df) + geom_bar(aes(x = diag_3))
ggplot(df) + geom_bar(aes(x = max_glu_serum))
ggplot(df) + geom_bar(aes(x = A1Cresult))
ggplot(df) + geom_bar(aes(x = metformin))
ggplot(df) + geom_bar(aes(x = repaglinide))
ggplot(df) + geom_bar(aes(x = nateglinide))
ggplot(df) + geom_bar(aes(x = chlorpropamide))
ggplot(df) + geom_bar(aes(x = glimepiride))
ggplot(df) + geom_bar(aes(x = acetohexamide))
ggplot(df) + geom_bar(aes(x = glipizide))
ggplot(df) + geom_bar(aes(x = glyburide))
ggplot(df) + geom_bar(aes(x = tolbutamide))
ggplot(df) + geom_bar(aes(x = pioglitazone))
ggplot(df) + geom_bar(aes(x = rosiglitazone))
ggplot(df) + geom_bar(aes(x = acarbose))
ggplot(df) + geom_bar(aes(x = miglitol))
ggplot(df) + geom_bar(aes(x = troglitazone))
ggplot(df) + geom_bar(aes(x = tolazamide))
ggplot(df) + geom_bar(aes(x = examide))
ggplot(df) + geom_bar(aes(x = citoglipton))
ggplot(df) + geom_bar(aes(x = insulin))
# ggplot(df) + geom_bar(aes(x = glyburide-metformin))
# ggplot(df) + geom_bar(aes(x = glipizide-metformin))
# ggplot(df) + geom_bar(aes(x = glimepiride-pioglitazone))
# ggplot(df) + geom_bar(aes(x = metformin-rosiglitazone))
# ggplot(df) + geom_bar(aes(x = metformin-pioglitazone))
ggplot(df) + geom_bar(aes(x = change))
ggplot(df) + geom_bar(aes(x = diabetesMed))
ggplot(df) + geom_bar(aes(x = readmitted))

```
```{r}

```



```{r}
#People
g1 = ggplot(diabetic_data) + geom_histogram(aes(x = time_in_hospital), bins = 500)
g1
g2 = ggplot(df) + geom_histogram(aes(x = age), bins = 3)
g3 = ggplot(df) + geom_histogram(aes(x = Teenhome), bins = 3)
g4 = ggplot(df) + geom_histogram(aes(x = Recency), bins = 50)
g18 = ggplot(diabetic_data) + geom_histogram(aes(x = age), bins = 5)
g18
g21 = ggplot(df) + geom_histogram(aes(x = Seniority),bins = 50)

g15 = ggplot(diabetic_data) + geom_bar(aes(x = age))
g15
```

---
title: "ISE-535 Final Projct -- Customer Personality Analysis"
author: "Group 09: Xuchen Shao, Haoyuan Zhang, Shejun Gao, Xi Pei"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# import library
library(tidyverse)
library(ggcorrplot)
library(clustertend)
library(gridExtra)
library(ggplot2)
library(arules)
library(arulesViz)

# reset file path
setwd("D:/STUDY/Graduate Program/MFE program/05-Semester Fa21/ISE-535 Data Mining/Homework/Final Project")

# summary function
# for numeric attributes
summarize_numeric = function(dataset) {
    dataset = select_if(dataset, is.numeric)
    summary.table = data.frame(Attribue = names(dataset))
    summary.table = summary.table %>% 
        mutate('Missing Values' = apply(dataset, 2, function(x) sum(is.na(x))),
               'Unique Values' = apply(dataset, 2, function(x) length(unique(x))),
               'Mean' = round(colMeans(dataset, na.rm = TRUE),2),
               'Min' = apply(dataset, 2, function(x) min(x, na.rm = TRUE)),
               'Max' = apply(dataset, 2, function(x) max(x, na.rm = TRUE)),
               'SD' = round(apply(dataset, 2, function(x) sd(x, na.rm = TRUE)),2))
    summary.table
    }

# for character attributes
summarize_character = function(dataset) {
    dataset = select_if(dataset, is.character)
    summary.table = data.frame(Attribue = names(dataset))
    summary.table = summary.table %>% 
        mutate('Missing Values' = apply(dataset, 2, function(x) sum(is.na(x))),
               'Unique Values' = apply(dataset, 2, function(x) length(unique(x))))
    summary.table
}

# winsorize

winsorize = function(data, end){
  endpoint = quantile(data, probs=c(end, 1-end), na.rm = T)
  data[data < endpoint[1]] = endpoint[1]
  data[data > endpoint[2]] = endpoint[2]
  return(data)
}

```



# DATA PROCESSING
```{r}
# import data file
df = read_csv("marketing_campaign.csv")
df

# initial data review
class(df)
str(df)
names(df)
summarize_numeric(df)
summarize_character(df)

```
```{r}
# initial data processing from raw data
df = df %>% 
  na.omit() %>% # drop missing value
  select(!c(ID,
            AcceptedCmp1,
            AcceptedCmp2,
            AcceptedCmp3,
            AcceptedCmp4,
            AcceptedCmp5,
            Z_CostContact,
            Z_Revenue
            )
         ) # drop irrelevant attributes

# winsorize  
df$Income = winsorize(df$Income,0.01)

# new attributes based on raw data
df$Age = 2014 - df$Year_Birth 
df$Seniority = as.numeric(as.Date("31-12-2014","%d-%m-%y")-as.Date(df$Dt_Customer,"%d-%m-%y"))
df = df %>% 
  select(-c(Year_Birth,Dt_Customer))

summarize_numeric(df)
summarize_character(df)
```

#univariate analysis
```{r}
#univariate analysis
#numeric attributes - People
g1 = ggplot(df) + geom_histogram(aes(x = Income), bins = 500)
g2 = ggplot(df) + geom_histogram(aes(x = Kidhome), bins = 3)
g3 = ggplot(df) + geom_histogram(aes(x = Teenhome), bins = 3)
g4 = ggplot(df) + geom_histogram(aes(x = Recency), bins = 50)
g18 = ggplot(df) + geom_histogram(aes(x = Age), bins = 5)
g21 = ggplot(df) + geom_histogram(aes(x = Seniority),bins = 50)

grid.arrange(g1, g2, g3, g4, g18, g21, nrow=3)

#numeric attributes - Products
g5 = ggplot(df) + geom_histogram(aes(x = MntWines), bins = 5)
g6 = ggplot(df) + geom_histogram(aes(x = MntFruits), bins = 5)
g7 = ggplot(df) + geom_histogram(aes(x = MntMeatProducts), bins = 5)
g8 = ggplot(df) + geom_histogram(aes(x = MntFishProducts), bins = 5)
g9 = ggplot(df) + geom_histogram(aes(x = MntSweetProducts), bins = 5)
g10 = ggplot(df) + geom_histogram(aes(x = MntGoldProds), bins = 5)
grid.arrange(g5, g6, g7, g8, g9, g10, nrow=3)

#numeric attributes - Promotion
ggplot(df) + geom_histogram(aes(x = NumDealsPurchases), bins = 20)

#numeric attributes - Place
g11 = ggplot(df) + geom_histogram(aes(x = NumWebPurchases), bins = 20)
g12 = ggplot(df) + geom_histogram(aes(x = NumCatalogPurchases), bins = 40)
g13 = ggplot(df) + geom_histogram(aes(x = NumStorePurchases), bins = 20)
g14 = ggplot(df) + geom_histogram(aes(x = NumWebVisitsMonth), bins = 20)
grid.arrange(g11, g12, g13, g14, nrow=2)

#categorical attributes - People
g15 = ggplot(df) + geom_bar(aes(x = Education))
g16 = ggplot(df) + geom_bar(aes(x = Marital_Status))
g17 = ggplot(df) + geom_bar(aes(x = as.factor(Complain) ))
g20 = ggplot(df) + geom_bar(aes(x = as.factor(Response)))
grid.arrange(g15, g16, g17, g20, nrow = 2)

#bivariate analysis
#create correlation plot and decide which attributes to drop
ggcorrplot(cor(df %>% select_if(is.numeric)), lab = F)

#measure & measure
#1. income versus expenditure on products
g1 = ggplot(df) + geom_point(aes(x = Income, y = MntWines))
g2 = ggplot(df) + geom_point(aes(x = Income, y = MntFruits))
g3 = ggplot(df) + geom_point(aes(x = Income, y = MntMeatProducts))
g4 = ggplot(df) + geom_point(aes(x = Income, y = MntFishProducts))
g5 = ggplot(df) + geom_point(aes(x = Income, y = MntSweetProducts))
g6 = ggplot(df) + geom_point(aes(x = Income, y = MntGoldProds))
grid.arrange(g1, g2, g3, g4, g5, g6, nrow = 2)
#As we can see, there are linear relationships between income and every expenditure on products, which is expected.

#2. income versus place of purchases
g1 = ggplot(df) + geom_point(aes(x = Income, y = NumWebPurchases))
g2 = ggplot(df) + geom_point(aes(x = Income, y = NumCatalogPurchases))
g3 = ggplot(df) + geom_point(aes(x = Income, y = NumStorePurchases))
g4 = ggplot(df) + geom_point(aes(x = Income, y = NumWebVisitsMonth))
grid.arrange(g1, g2, g3, g4, nrow = 2)

#measure & category
#1. income versus education
ggplot(df) + geom_boxplot(aes(x = Education, y = Income))

#2. income versus marital status
ggplot(df) + geom_boxplot(aes(x = Marital_Status, y = Income))


#category & category
ggplot(df) + geom_bar(aes(x= Education, fill = Marital_Status), position = "fill") + labs(y = "Percent")
ggplot(df) + geom_bar(aes(x= Marital_Status, fill = Education), position = "fill") + labs(y = "Percent")

```


# Model 01 Multiple Regression Analysis
```{r}
# model 01
# extra data processing for model 01
model_01 = df

model_01$Spending = model_01$MntWines + 
                    model_01$MntFruits + 
                    model_01$MntMeatProducts + 
                    model_01$MntFishProducts + 
                    model_01$MntSweetProducts + 
                    model_01$MntGoldProds
model_01$Kid = model_01$Kidhome + 
               model_01$Teenhome

# model_01 %>% group_by(model_01$Marital_Status) %>% summarise(n= n())
model_01$Marital_Status = replace(model_01$Marital_Status,model_01$Marital_Status == "Divorced","0")
model_01$Marital_Status = replace(model_01$Marital_Status,model_01$Marital_Status == "Single","0")
model_01$Marital_Status = replace(model_01$Marital_Status,model_01$Marital_Status == "Absurd","0")
model_01$Marital_Status = replace(model_01$Marital_Status,model_01$Marital_Status == "Widow","0")
model_01$Marital_Status = replace(model_01$Marital_Status,model_01$Marital_Status == "YOLO","0")
model_01$Marital_Status = replace(model_01$Marital_Status,model_01$Marital_Status == "Alone","0")
model_01$Marital_Status = replace(model_01$Marital_Status,model_01$Marital_Status == "Married","1")
model_01$Marital_Status = replace(model_01$Marital_Status,model_01$Marital_Status == "Together","1")
model_01$Marital_Status = as.numeric(model_01$Marital_Status)

# model_01 %>% group_by(model_01$Education) %>% summarise(n= n())
model_01$Education = replace(model_01$Education,model_01$Education == "2n Cycle","0")
model_01$Education = replace(model_01$Education,model_01$Education == "Basic","0")
model_01$Education = replace(model_01$Education,model_01$Education == "Graduation","1")
model_01$Education = replace(model_01$Education,model_01$Education == "Master","1")
model_01$Education = replace(model_01$Education,model_01$Education == "PhD","1")
model_01$Education = as.numeric(model_01$Education)

model_01 = model_01 %>%
  select(-c(Kidhome,Teenhome))

class(model_01)
str(model_01)
names(model_01)

write.csv(model_01,"model_01.csv")
```
```{r}
fit.Spend = glm(Spending ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Spend)

fit.Wine = glm(MntWines ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Wine)
fit.Fruit = glm(MntFruits ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Fruit)
fit.Meat = glm(MntMeatProducts ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Meat)
fit.Fish = glm(MntFishProducts ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Fish)
fit.Sweet = glm(MntSweetProducts ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Sweet)
fit.Gold = glm(MntGoldProds ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Gold)

fit.Deal = glm(NumDealsPurchases ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Deal)
fit.Web = glm(NumWebPurchases ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Web)
fit.Catalog = glm(NumCatalogPurchases ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Catalog)
fit.Store = glm(NumStorePurchases ~ Education+Marital_Status+Income+Recency+Complain+NumWebVisitsMonth+Age+Seniority+Kid, data = model_01)
summary(fit.Store)
```

# Model 02 Logistic Regression Analysis

```{r}
# model 02
# extra data processing for model 02
model_02 = df

model_02$Spending = model_02$MntWines + 
                    model_02$MntFruits + 
                    model_02$MntMeatProducts + 
                    model_02$MntFishProducts + 
                    model_02$MntSweetProducts + 
                    model_02$MntGoldProds
model_02$Kid = model_02$Kidhome + model_02$Teenhome
model_02$Kid = replace(model_02$Kid,model_02$Kid != 0,1)

# model_02 %>% group_by(model_02$Marital_Status) %>% summarise(n= n())
model_02$Marital_Status = replace(model_02$Marital_Status,model_02$Marital_Status == "Divorced","0")
model_02$Marital_Status = replace(model_02$Marital_Status,model_02$Marital_Status == "Single","0")
model_02$Marital_Status = replace(model_02$Marital_Status,model_02$Marital_Status == "Absurd","0")
model_02$Marital_Status = replace(model_02$Marital_Status,model_02$Marital_Status == "Widow","0")
model_02$Marital_Status = replace(model_02$Marital_Status,model_02$Marital_Status == "YOLO","0")
model_02$Marital_Status = replace(model_02$Marital_Status,model_02$Marital_Status == "Alone","0")
model_02$Marital_Status = replace(model_02$Marital_Status,model_02$Marital_Status == "Married","1")
model_02$Marital_Status = replace(model_02$Marital_Status,model_02$Marital_Status == "Together","1")
model_02$Marital_Status = as.numeric(model_02$Marital_Status)

# model_02 %>% group_by(model_02$Education) %>% summarise(n= n())
model_02$Education = replace(model_02$Education,model_02$Education == "2n Cycle","0")
model_02$Education = replace(model_02$Education,model_02$Education == "Basic","0")
model_02$Education = replace(model_02$Education,model_02$Education == "Graduation","1")
model_02$Education = replace(model_02$Education,model_02$Education == "Master","1")
model_02$Education = replace(model_02$Education,model_02$Education == "PhD","1")
model_02$Education = as.numeric(model_02$Education)

summarize_numeric(model_02)

model_02 = model_02 %>%
  select(c(Education,Marital_Status,Income,Recency,Complain,Response,NumDealsPurchases,NumWebPurchases,NumCatalogPurchases,NumStorePurchases,NumWebVisitsMonth,Age,Spending,Seniority,Kid))

summarize_numeric(model_02)

fit.Logit = glm(data = model_02, Response ~Education+Marital_Status+Income+Recency+Complain+NumDealsPurchases+NumWebPurchases+NumCatalogPurchases+NumStorePurchases+NumWebVisitsMonth+Age+Spending+Seniority+Kid,family = binomial(link = "logit"))

summary(fit.Logit)
```

```{r}
# model 03 
model_03 = df
model_03

#drop irrelevant attributes
model_03 = subset(model_03, select = -c(Response, Seniority, Age))
names(model_03)

#make categorical attributes as factors
model_03 = model_03 %>% mutate( Education = as.factor(Education),
                                Marital_Status = as.factor(Marital_Status),
                                Complain = as.factor(Complain))

#display categories(factors)
colnames(model_03 %>% select_if(is.factor))

#display numeric variables(measures)
colnames(model_03 %>% select_if(is.numeric))

#Adding binary variables for Education
model_03 %>% count(Education)
model_03_binary = model_03 %>% mutate(Education_2n_Cycle = 
                                        if_else(Education == "2n Cycle", 1, 0))
model_03_binary = model_03_binary %>% mutate(Education_Basic = 
                                        if_else(Education == "Basic", 1, 0))
model_03_binary = model_03_binary %>% mutate(Education_Graduation = 
                                        if_else(Education == "Graduation", 1, 0))
model_03_binary = model_03_binary %>% mutate(Education_Master = 
                                        if_else(Education == "Master", 1, 0))
model_03_binary = model_03_binary %>% mutate(Education_PhD = 
                                        if_else(Education == "PhD", 1, 0))


#Adding binary variables for Marital Status
model_03 %>% count(Marital_Status)
model_03_binary = model_03_binary %>% mutate(Marital_Status_Absurd = 
                                        if_else(Marital_Status == "Absurd", 1, 0))
model_03_binary = model_03_binary %>% mutate(Marital_Status_Alone = 
                                        if_else(Marital_Status == "Alone", 1, 0))
model_03_binary = model_03_binary %>% mutate(Marital_Status_Divorced = 
                                        if_else(Marital_Status == "Divorced", 1, 0))
model_03_binary = model_03_binary %>% mutate(Marital_Status_Married =
                                        if_else(Marital_Status == "Married", 1, 0))
model_03_binary = model_03_binary %>% mutate(Marital_Status_Single = 
                                        if_else(Marital_Status == "Single", 1, 0))
model_03_binary = model_03_binary %>% mutate(Marital_Status_Together = 
                                        if_else(Marital_Status == "Together", 1, 0))
model_03_binary = model_03_binary %>% mutate(Marital_Status_Widow = 
                                        if_else(Marital_Status == "Widow", 1, 0))
model_03_binary = model_03_binary %>% mutate(Marital_Status_YOLO = 
                                        if_else(Marital_Status == "YOLO", 1, 0))


#scale the data
model_03_binary_scaled = scale(model_03_binary %>% select_if(is.numeric))

#calculate Hopkins statistic
hopkins(model_03_binary_scaled, 10)
#Since the value is significantly less than 0.5, there exists a high clusterability

#create elbow chart
model_03_scaled = scale(model_03 %>% select_if(is.numeric))
totwss = tibble(num_clusters = 1:10, tot_withinss = 0)
for (i in 1:10) {
  km = kmeans(model_03_scaled, i, nstart = 10)
  totwss$tot_withinss[i] = km$tot.withinss
}
ggplot(totwss, aes(x = num_clusters, y=tot_withinss)) + geom_line() + geom_point()
#based on the elbow chart, 3 clusters seem to be the best choice
 
#generate and describe clusters
km_market = kmeans(model_03_binary_scaled, 3, nstart = 10)
model_03 = model_03 %>% mutate(Cluster = as_factor(km_market$cluster))
Mode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}
cluster_summary <- model_03 %>% group_by(Cluster) %>% summarize(Size = n(), Income = mean(Income), Kidhome = mean(Kidhome), 
                                              Teenhome = mean(Teenhome), Recency = mean(Recency), MntWines = mean(MntWines),
                                              MntFruits = mean(MntFruits), MntMeatProducts = mean(MntMeatProducts), MntFishProducts = mean(MntFishProducts),
                                              MntSweetProducts = mean(MntSweetProducts), MntGoldProds = mean(MntGoldProds), NumDealsPurchases = mean(NumDealsPurchases),
                                              NumWebPurchases = mean(NumWebPurchases), NumCatalogPurchases = mean(NumCatalogPurchases), NumStorePurchases = mean(NumStorePurchases),
                                              NumWebVisitsMonth = mean(NumWebVisitsMonth), Education = Mode(Education), Marital_Status = Mode(Marital_Status),
                                              Complain = Mode(Complain))
print.data.frame(cluster_summary)
#cluster1: High income, no kid, no teen, high expenditure on fruit, meat, fish, sweet, gold, low discount purchase deals,  high web purchase deals, high catalogue purchase, high store purchase, low webvisit, graduation, married
#cluster2: Low income, has one kid home, no teen home, low expenditure on wine, fruit, meat, fish, sweet and gold products, medium discount purchase, low web purchase, low catalogue purchase, low store purchase, high web visit, graduation, married
#cluster3: Middle income, no kid home, one teen home, high expenditure on wine, meat and gold products, low expenditure on fruit, fish and sweet products, high discount purchase deals, web purchase, medium catalog purchase, high store purchase, high web visit, graduation, married. 
```

# model 04
```{r}
# model 04
# extra data processing for model 02

model_04 = df
model_04 = model_04 %>%
  select(c("MntWines", "MntFruits", "MntMeatProducts", "MntFishProducts", "MntSweetProducts", "MntGoldProds"))
model_04

txt = data.frame(items = character(2216))
txt

for (i in 1:2216) {
  wine = rep('wine', as.numeric(model_04[i,1]))
  fruit = rep('fruit', as.numeric(model_04[i,2]))
  meat = rep('meat', as.numeric(model_04[i,3]))
  fish = rep('fish', as.numeric(model_04[i,4]))
  sweet = rep('sweet', as.numeric(model_04[i,5]))
  gold = rep('gold', as.numeric(model_04[i,6]))
  a = c(wine, fruit, meat, fish, sweet, gold)
  length(a)
  vector = a[1]
  for (j in 2:length(a)) {
    vector = paste(vector,a[j], sep = " ")
  }
  txt[i,1] = vector
  print(i)
}

txt

transactions = write.table(txt, 'products.txt', sep = " ", row.names = F, col.names = F)
transactions = read.transactions("products.txt")

summary(transactions)
image(sample(transactions, 50))
#item frequency plots
itemFrequencyPlot(transactions)

associa_rules = apriori(data = transactions, parameter = list(support = 0.5, confidence = 0.8))

#visualising the results
inspect(associa_rules, by = "lift")
plot(associa_rules, method = 'graph', measure = 'confidence', shading = 'lift')

```


```{r}
# associa_rules = apriori(data = transactions, parameter = list(support = 0.9, confidence = 0.8))
```

```{r }
#visualising the results
#inspect(associa_rules, n = 3, by = "lift")
#plot(associa_rules, method = 'graph', measure = 'confidence', shading = 'lift')
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.






```